Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Added some images to manus

  \subsection{Parameter Values and Justification}
    Using our earlier values for the maximum flow rate of an edge, we can now use this
  \subsection{Results}
  \subsection{Strengths and Weaknesses}
    By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.

>>>>

  \subsection{Parameter Values and Justification}
    Using our earlier values for the maximum flow rate of an edge, we can now use this
  \subsection{Results}
    % TODO
      Figure~\ref{fig:pop_deter} shows the evolution of the populations of some example states during an evacuation. The Y-Axis shows the percentage of the original population is contained in that state, and the X-Axis is the number of hours that has elapsed since the evacuation order.
    \begin{figure}
      \center
      \begin{subfigure}[b]{0.3\textwidth}
        \center
        \includegraphics[width=\textwidth]{figures/pop_county_29-crop.pdf}
        \caption{Population of Jackson}
        \label{fig:pop_county60}
      \end{subfigure}~
      \begin{subfigure}[b]{0.3\textwidth}
        \center
        \includegraphics[width=\textwidth]{figures/pop_county_39-crop.pdf}
        \caption{Population of Leake}
        \label{fig:pop_county39}
      \end{subfigure}~
      \begin{subfigure}[b]{0.3\textwidth}
        \center
        \includegraphics[width=\textwidth]{figures/pop_county_60-crop.pdf}
        \caption{Population of Rankin}
        \label{fig:pop_county60}
      \end{subfigure}
      \caption{Evolution of populations during evacuation}
      \label{fig:pop_deter}
    \end{figure}
    % TODO
    % We tested against all 15 hurricanes
    % For 14 of the 15 hurricanes, we managed to have the time to evacuation under 80 minutes.
    % One hurricane (category 5) made the evacuation take longer than 100 days --> order evacuation imediately as soon as we see a cat 5

  \subsection{Strengths and Weaknesses}
    % We can get an estimate of how long we need to evacuate based on the specs of the hurricane
    % Its not a one-size-fits all which is good and bad
    By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.
